Bayesian statistics and swine flu

### 2009-08-14 docs/pandemic/bayesPandemic.rnw
fixed chain mixing
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/diseasemapping@360 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

\begin{frame}[fragile]
\frametitle{Simulated data}
<<simData,echo=true,fig=false>>=
params = pandemicParams( 
	InfOns = c(mean=1.5, shape=2, zeros=.1),
	OnsMedM= c(mean=1, shape=1, zeros=.1 ),
	OnsMedS= c(mean=1, shape=1, zeros=.1 ),
	OnsMedD= c(mean=1, shape=1, zeros=.1 ),
	MedRec = c(mean=3, shape=2, zeros=.1, lost=0.95 ),
  MedHospS = c(mean = 2, shape = 2, zeros = 0.1),
  MedHospD = c(mean = 2, shape = 2, zeros = 0.1),
	HospRec = c(mean=2, shape=1.5, zeros=.01 ),
	HospDeath = c(mean=2, shape=0.1, zeros=.05 ),
 	probs = c(M=0.7, S=0.25, D=0.05)
  )

@@

\begin{frame}[fragile]
\frametitle{Results}
<<mcmcResults,echo=true,fig=false>>=
paramSample = mcmcPandemic(data,params,priors,sigma=0.05,runs=600)
paramSample = paramSample[seq(100,dim(paramSample)[1], by=5),]
dim(paramSample)
colnames(paramSample)
@
\end{frame}

>>>>

\begin{frame}[fragile]
\frametitle{Simulated data}
<<simData,echo=true,fig=false>>=
params = pandemicParams( 
	InfOns = c(mean=1.5, shape=2, zeros=.1),
	OnsMedM= c(mean=1, shape=1, zeros=.1 ),
	OnsMedS= c(mean=1, shape=1, zeros=.1 ),
	OnsMedD= c(mean=1, shape=1, zeros=.1 ),
	MedRec = c(mean=3, shape=2, zeros=.1, lost=0.95 ),
  MedHospS = c(mean = 2, shape = 2, zeros = 0.1),
  MedHospD = c(mean = 2, shape = 2, zeros = 0.1),
	HospRec = c(mean=2, shape=1.5, zeros=.01 ),
	HospDeath = c(mean=2, shape=0.8, zeros=.05 ),
 	probs = c(M=0.7, S=0.25, D=0.05)
# 	probs = c(M=0.979, S=0.02, D=0.001)
  )

@@

\begin{frame}[fragile]
\frametitle{Results}
<<mcmcResults,echo=true,fig=false>>=
scale = mcmcScale(params, 0.075,minScale = 0.05 )
paramSample = mcmcPandemic(data,params,priors,sigma=scale,runs=60)
paramSample = paramSample[seq(100,dim(paramSample)[1], by=5),]
dim(paramSample)
colnames(paramSample)
@
\end{frame}
